\documentclass[10pt,letterpaper]{article}

% -------------------- Packages --------------------
\usepackage[left=0.65in, right=0.65in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{parskip}
\usepackage{setspace}

% -------------------- Styling --------------------
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=2pt, parsep=0pt}

\titleformat{\section}
  {\large\bfseries}
  {}{0em}{}
  [\titlerule]

\titlespacing*{\section}{0pt}{8pt}{6pt}

\newcommand{\eduEntry}[4]{
  \begin{tabularx}{\textwidth}{X r}
    \textbf{#1} & #2 \\
  \end{tabularx}
  \vspace{-2pt}
  \hspace*{0.15in}#3 \hfill #4
  \vspace{4pt}
}


% A compact "entry" layout: left = role/company, right = date
\newcommand{\resumeEntry}[2]{
  \begin{tabularx}{\textwidth}{X r}
    \textbf{#1} & #2 \\
  \end{tabularx}
  \vspace{-18pt}
}
% Like above but without italic subtitle line
\newcommand{\resumeEntrySimple}[2]{
  \begin{tabularx}{\textwidth}{X r}
    \textbf{#1} & #2 \\
  \end{tabularx}
}

\begin{document}

% -------------------- Header --------------------
\begin{center}
    {\LARGE \textbf{Andrew Snowdy}} \\[4pt]
    \textit{U.S. Citizen} \;\;|\;\;
    \href{mailto:Drewsnowdy19@gmail.com}{Drewsnowdy19@gmail.com} \;\;|\;\;
     (716) 228--7038 \;\;|\;\;
    \href{https://andrewsnowdy.github.io/}{Portfolio} \;\;|\;\;
    \href{https://www.linkedin.com/in/andrew-snowdy-2a9833258/}{LinkedIn} \;\;|\;\;
    \href{https://github.com/AndrewSnowdy}{GitHub}
\end{center}


\vspace{2pt}

% -------------------- Education --------------------
\section*{Education}

\eduEntry{Gannon University}{Graduated May 2024}
{B.S. in Electrical Engineering, Minor in Mathematics}{GPA: 3.9 / 4.0}

\eduEntry{Northeastern University}{Expected Graduation: May 2026}
{M.S. in Electrical and Computer Engineering}{GPA: 3.7 / 4.0}
% -------------------- Experience --------------------
\section*{Relevant Experience}

\resumeEntry{Research Assistant -- Northeastern University}{March 2025 -- Present}
\begin{itemize}[leftmargin=0.3in, topsep=0pt, itemsep=2pt, parsep=0pt]
  \item NEURoam: Architected a unified data acquisition platform for a diverse robotic fleet; implemented hardware-level synchronization (PPS/NMEA) across LiDAR, GPS, IMU, stereo cameras and radios on NVIDIA Jetson Orin to enable campus-scale 3D mapping. Expanded to a 5-robot mesh network.
  \item NEUFlow: Integrated stereo mapping and optical-flow pipeline on Jetson for UAV autonomy; benchmarked latency and throughput to support real-time obstacle avoidance.
\end{itemize}

\resumeEntry{Moog -- Aircraft Group Internship}{May 2023 -- January 2025}
\begin{itemize}[leftmargin=0.3in, topsep=2pt, itemsep=2pt, parsep=0pt]
    \item Supported qualification testing of hydraulic control modules, power drive units, and actuators, executing functional and environmental procedures to meet FAA certification requirements.
    \item Automated Gulfstream test-stand data processing in MATLAB and VBA, enabling anomaly identification and reducing manual reporting effort across the group.
\end{itemize}

\resumeEntry{Research Assistant -- Gannon University}{August 2021 -- May 2024}
\begin{itemize}[leftmargin=0.3in, topsep=2pt, itemsep=2pt, parsep=0pt]
  \item Served as technical lead for NASA/NSF NEBP to design and deploy stratospheric balloon payloads, equipped with a multi-node communication system using Iridium satellite links and an XBee mesh network. 
  \item Reverse-engineered legacy hardware to design custom PCBs in Altium for altitude control; integrated servos and sensor stacks for real-time flight diagnostics.
  \item Developed a high-altitude payload using C++ and Python, and rectified a legacy ground-station receiver for 5.8 GHz Rocket M5 video and RFD 900 MHz telemetry downlinks.
\end{itemize}

\resumeEntry{Niagara Refining LLC -- Electrical Engineering Internship}{May -- August 2022}
\begin{itemize}[leftmargin=0.3in, topsep=0pt, itemsep=2pt, parsep=0pt]
    \item Programmed VFDs and Siemens PLC systems for industrial equipment upgrades and preventative maintenance.
    \item Configured Modbus/Profinet/ethernet communications and diagnosed control hardware to reduce downtime, supporting sensor replacement and electrical renovations.

\end{itemize}


% \resumeEntry{Lab Operation Assistant -- Gannon University}{August 2021 -- May 2024}{}
% \begin{itemize}[leftmargin=0.3in, topsep=2pt, itemsep=2pt, parsep=0pt]
%   \item Collaborated with faculty and graduate students to set up an industrial PCB production line; programmed Kayo Pick \& Place and heating bed using Altium and embedded software.
%   \item Assisted in labs; assembled PCs/microcontrollers and organized components.
% \end{itemize}

% \resumeEntry{Teacher's Assistant -- Circuits Class}{January -- May 2022}{}
% \begin{itemize}[leftmargin=0.3in, topsep=2pt, itemsep=2pt, parsep=0pt]
%   \item Supported students in lecture and lab to complete circuit analysis and build tasks; taught and demonstrated examples for a class of 20 students.
% \end{itemize}


% -------------------- Projects -------------------


% \resumeEntry{President of IEEE Club}{August 2022 -- May 2024}{}
% \begin{itemize}
%   \item Attend conferences, compete in robotic events and written contests.
% \end{itemize}

% \resumeEntry{Intelligent Ground Vehicle}{August 2022 -- Dec 2023}{}
% \begin{itemize}
%   \item Design a vehicle to autonomously navigate while carrying a heavy payload.
% \end{itemize}
% \textbf{Nixie Tube Build} --- Designed PCB with integrated Arduino/Teensy and other IC.

\section*{Selected Technical Projects}

\resumeEntry{Master's Project -- Autonomous Mobile Manipulation on Toyota HSR}{2025 -- Present}
\begin{itemize}[leftmargin=0.3in, topsep=0pt, itemsep=2pt, parsep=0pt]
    \item Developed a ROS 2 navigation-manipulation stack enabling a Toyota HSR to approach and activate ADA door buttons in Gazebo and on hardware using TF-based alignment and waypoints.
  \item Implemented Damped Least Squares IK and quintic splines for smooth trajectory generation.
\end{itemize}


\resumeEntry{Unitree Go2 Control \& Estimation}{2024 -- Present}
\begin{itemize}[leftmargin=0.3in, topsep=0pt, itemsep=2pt, parsep=0pt]
\item Derived a C++ Whole-Body Controller solving a Quadratic Program at 500Hz to regulate centroidal dynamics while enforcing friction cone and contact constraints.
  \item Established an 800Hz Extended Kalman Filter  to track floating-base pose and velocity by fusing high-frequency IMU data with leg kinematics via contact-point updates.
\end{itemize}


\resumeEntry{Robotic Arm Build -- Perception \& Control}{2023 -- 2024}
\begin{itemize}[leftmargin=0.3in, topsep=0pt, itemsep=2pt, parsep=0pt]
  \item Built a low-cost, 6-DOF, 3D-printed robotic arm with closed-loop control over CAN, integrating custom gearboxes (harmonic, cycloidal, planetary) and gripper force feedback for contact detection.
\end{itemize}

% \resumeEntry{Undergraduate Capstone -- Black-Start Control for Inverter-Based Microgrids}{2023 -- 2024}
% \begin{itemize}[leftmargin=0.3in, topsep=0pt, itemsep=2pt, parsep=0pt]
%   \item Designed and implemented a grid-forming inverter control scheme for black-starting inverter-based microgrids using droop control, dq-frame control loops, and PWM on a TI C2000 (F28379D) platform.
% \end{itemize}

 
% -------------------- Skills --------------------
\section*{Skills}

\begin{multicols}{4}
\begin{itemize}
  \item C++, Python, C
  \item CMake, Eigen, Pinocchio
  \item ROS 2, DDS, Linux
  \item QP-based Control
  \item EKF, State Estimation
  \item MuJoCo / Gazebo
  \item Git / Subversion
  \item MATLAB, Simulink
  \item CAN, UART, I2C
  \item Chrony, GNSS, NMEA
  \item Altium, KiCad
  \item Fusion 360
\end{itemize}
\end{multicols}

% \textbf{Basic Understand:}
% \begin{multicols}{2}
% \begin{itemize}
%   \item VHDL/VCIM
%   \item PSpice
%   \item Java
%   \item SQL
% \end{itemize}
% \end{multicols}

\end{document}
